---
title: ""
output: html_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(plotly)
source("scripts/dataframe.R")
#Select the most expensive additional class
most.expensive.additional <- improved.df %>% filter(new.additional == max(new.additional))

#Longest time of the class
longest.time.class <- improved.df %>% filter(is.na(time_diff) == FALSE) %>% filter(time_diff == max(time_diff))

#Most Capacity
most.capacity <- improved.df %>% filter(is.na(Capacity) == FALSE) %>% filter(Capacity == max(Capacity))

#very expensive small capacity class
expensive.smallest.capacity <- improved.df %>% filter(is.na(Capacity) == FALSE & Capacity != 0) %>% filter(Capacity < 5 & new.additional > 1000)


```

#### Most expensive additional class
The most expensive additional class is *`r most.expensive.additional$Course[1]`* which have additional fees of *`r most.expensive.additional$Additional[1]`*.

#### Longest class EVER!!
The longest class time is *`r longest.time.class$time_diff[1]`min*, which is *`r longest.time.class$Course[1]`*.

#### Most capacity class
The biggest capacity a class can hold is *`r most.capacity$Capacity[1]`*. And the classes are *`r most.capacity$Course`*.

####Very expensive small capacity classes
An interesting fact is that the classes that have the additional fees higher than *$1000* and class capacity smaller than *5* are all in **LAW SCHOOL**.

#### Here is a distribution of classes of different credits

```{r, echo=FALSE, warning=FALSE, message=FALSE}
pie <- ggplot(new.improved.credit, aes(x = factor(1), fill = factor(new.improved.credit$credits))) +  geom_bar(width = 1) 
p <- pie + coord_polar(theta = "y")
p
```