---
title: "Fun Facts"
output: html_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(stringr)
library(plotly)
library(ggplot2)

source("scripts/dataframe.R")

improved.df <- df
improved.df$new.additional <- substring(improved.df$Additional, 2)
improved.df$new.additional <- ifelse(improved.df$new.additional != "", as.numeric(gsub(",", "", improved.df$new.additional)), 0)


#Select the most expensive additional class
most.expensive.additional <- improved.df %>% filter(new.additional == max(new.additional))

#Longest time of the class
longest.time.class <- improved.df %>% filter(is.na(time_diff) == FALSE) %>% filter(time_diff == max(time_diff))

#Most Capacity
most.capacity <- improved.df %>% filter(is.na(Capacity) == FALSE) %>% filter(Capacity == max(Capacity))

#very expensive small capacity class
expensive.smallest.capacity <- improved.df %>% filter(is.na(Capacity) == FALSE & Capacity != 0) %>% filter(Capacity < 5 & new.additional > 1000)
```

# Most expensive additional class
The most expensive additional class is *`r most.expensive.additional$Course`* which have additional fees of *`r most.expensive.additional$Additional[1]`*.

# Longest class EVER!!
The longest class time is *`r longest.time.class$time_diff[1]`min*, which is *`r longest.time.class$Course[1]`*.

# Most capacity class
The biggest capacity a class can hold is *`r most.capacity$Capacity[1]`*. And the classes are *`r most.capacity$Course`*.

#Very expensive small capacity classes
An interesting fact is that the classes that have the additional fees higher than *$1000* and class capacity smaller than *5* are all in **LAW SCHOOL**.

## Here is a distribution of classes of different credits
```{r, echo=FALSE, message=FALSE, warning=FALSE}
improved.df$credits <- as.numeric(improved.df$Sub.Credit)
new.improved.credit <-improved.df %>% select(Course, credits) %>% filter(!is.na(credits), !credits == 0.0) %>% distinct()

data <- new.improved.credit %>% group_by(credits) %>% summarise(num = n())
colors <- c('rgb(211,94,96)', 'rgb(128,133,133)', 'rgb(144,103,167)', 'rgb(171,104,87)', 'rgb(114,147,203)')

p <- plot_ly(data, labels = ~credits, values = ~num, type = 'pie',
             textposition = 'inside',
             textinfo = 'label+percent',
             insidetextfont = list(color = '#FFFFFF'),
             hoverinfo = 'text',
             text = ~paste(credits, ' credits classes'),
             marker = list(colors = colors,
                           line = list(color = '#FFFFFF', width = 1)),
             #The 'pull' attribute can also be used to create space between the sectors
             showlegend = FALSE) %>%
  layout(title = 'UW Classes credits distribution',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
p
```